---
title: "Module Name"
module_code: "MODULE CODE"
author: "Module Coordinator Name"
department: "Department Name"
faculty: "Faculty of Science"
institution: "Nelson Mandela University"
date: "`r format(Sys.Date(), '%B %Y')`"

# Enable professional cover page with NMU branding
cover_page: true

format:
  docx:
    toc: true
    reference-doc: _extensions/nmu/module-guide/reference-doc.docx
    filters:
      - _extensions/nmu/module-guide/cover-page.lua
      - _extensions/nmu/module-guide/custom-styles.lua
    # Official NMU Science template styles are applied automatically
    # Colors: Green #006B34, Dark Blue #18324B, Purple #6C284F
    # Fonts: Arial for body and headings

execute:
  echo: true
  warning: true
  message: false

# NOTE: Custom blocks (:::  {.learning-outcome}, {.alert}, {.note}, etc.) 
# automatically render with proper NMU styling. Bold prefixes are added 
# automatically by the template - no need to include them manually.
---

# 1. INTRODUCTION {#introduction .unnumbered}

## 1.1 Welcome

Dear Student,

Welcome to **`{{Module Name}}`**. This learner guide is designed to support you throughout the semester by providing you with essential information about the module, including its aims, learning outcomes, assessment schedule, and learning resources.

::: {.learning-outcome}
After reading this guide, you will understand:
- The module's purpose and how it fits into your programme
- What is expected of you as a student
- How you will be assessed
- The resources available to support your learning
:::

## 1.2 Educational Approach

This module is underpinned by the principle of constructive alignment (Biggs), meaning that learning activities, assessments, and outcomes are carefully aligned to promote deep learning and critical thinking.

## 1.3 Responsibilities of the Student

You are expected to:

- Attend all scheduled classes and participate actively
- Prepare for sessions by completing prescribed readings and activities
- Engage with online platforms (e.g., Moodle/SharePoint)
- Submit assessments by the stipulated deadlines
- Familiarise yourself with institutional, faculty, and departmental rules

::: {.important}
**Attendance Requirement:** Regular attendance is essential for success in this module. Missing more than 20% of classes may result in a DP (Duly Performed) refusal.
:::

# 2. ADMINISTRATIVE INFORMATION {#admin .unnumbered}

## 2.1 Communication Channels

All communication relating to this module will take place through:

- **Moodle**: Course announcements, resources, and discussion forums
- **Mandela University Email**: Official communications

::: {.tip}
**Tip:** Check your Mandela University email daily. All official communication will be sent to this address.
:::

## 2.2 Contact Details

**Module Coordinator:** `{{Name}}`

**Office Location:** `{{Building and Room Number}}`

**Office Hours:** `{{Days and Times}}`

**Email:** `{{Email Address}}`

**Telephone:** `{{Number}}`

# 3. MODULE INFORMATION {#module-info .unnumbered}

## 3.1 Module Description and Purpose

This module aims to `{{brief description aligned to yearbook}}`. It contributes to the programme by developing your knowledge, skills, and competencies in `{{specific area}}`.

::: {.key-point}
**Module Focus:** This module emphasizes practical application of theoretical concepts through hands-on activities and real-world examples.
:::

## 3.2 Assumed Knowledge and Skills

On entering this module, you are expected to have:

- Foundational knowledge relevant to the discipline
- Basic academic literacy and digital skills
- Willingness to engage in independent and collaborative learning

## 3.3 NQF Level, Credits and Notional Hours

```{r}
# Module metadata
module_info <- data.frame(
  Attribute = c("Module Code", "Module Name", "NQF Level", "Credits", "Notional Hours"),
  Value = c("`{{Module Code}}`", "`{{Module Name}}`", "`{{Level}}`", "`{{Credits}}`", "`{{Hours}}`")
)

knitr::kable(module_info, caption = "Module Information")
```

## 3.4 Articulation with Other Modules

This module:

- **Pre-requisites:** `{{if applicable}}`
- **Co-requisites:** `{{if applicable}}`
- **Is a pre-requisite for:** `{{if applicable}}`
- **Forms part of:** `{{year/semester}} of the {{programme name}}`

## 3.5 Module Learning Outcomes

On successful completion of this module, you will be able to:

::: {.learning-outcome}
1. `{{Outcome 1 - knowledge-based}}`

2. `{{Outcome 2 - skill-based}}`

3. `{{Outcome 3 - application-based}}`

4. `{{Outcome 4 - critical thinking}}`

5. `{{Outcome 5 - professional practice}}`
:::

These outcomes are aligned to programme outcomes and graduate attributes.

## 3.6 Module Structure and Content

The module is structured around `{{number}}` main themes/topics:

```{r}
# Topic structure
topics <- data.frame(
  Topic = c("Topic 1", "Topic 2", "Topic 3", "Topic 4"),
  Description = c(
    "`{{Description}}`",
    "`{{Description}}`",
    "`{{Description}}`",
    "`{{Description}}`"
  ),
  Duration = c("`{{Weeks}}`", "`{{Weeks}}`", "`{{Weeks}}`", "`{{Weeks}}`")
)

knitr::kable(topics, caption = "Module Structure")
```

# 4. PROFESSIONAL BODY REQUIREMENTS {#professional .unnumbered}

::: {.alert}
**Where applicable:** This module complies with the requirements of `{{Professional Body}}`.

All learning outcomes and assessments are aligned to the professional standards set by `{{Professional Body}}`.
:::

# 5. TEACHING & LEARNING DETAILS {#teaching .unnumbered}

## 5.1 Overview of Learning Activities

Your learning in this module will involve a range of activities including:

- **Lectures** (face-to-face / online)
- **Tutorials** and discussions
- **Practical or applied tasks**
- **Independent and group work**
- **Online activities** via Moodle

**Primary learning mode:** `{{Face-to-face / Online / Blended}}`

## 5.2 Weekly Schedule

```{r}
# Weekly schedule
weekly_schedule <- data.frame(
  Week = 1:14,
  Topic = c(
    "`{{Topic}}`", "`{{Topic}}`", "`{{Topic}}`", "`{{Topic}}`",
    "`{{Topic}}`", "**Test 1**", "`{{Topic}}`", "`{{Topic}}`",
    "`{{Topic}}`", "`{{Topic}}`", "**Project Due**", "`{{Topic}}`",
    "`{{Topic}}`", "Review"
  ),
  `Learning Activities` = c(
    "Lecture, Discussion", "Workshop, Group Exercise",
    "Lecture, Case Studies", "Lab Session, Design Exercise",
    "Demonstration, Practice", "", "Lecture, Computer Lab",
    "Lecture, Problem Set", "Lecture, Problem Set",
    "Workshop, Writing Exercise", "", "Student Presentations",
    "Seminar, Case Discussion", "Review Session"
  ),
  Assessment = c(
    "", "", "", "", "", "Test 1 (15%)", "", "", "", "", "Project (25%)", "", "", ""
  )
)

knitr::kable(weekly_schedule, caption = "Weekly Schedule and Assessment Plan")
```

::: {.activity}
**Activity:** Complete the weekly readings before class. Active participation in discussions is expected and will contribute to your class mark.
:::

# 6. LEARNING RESOURCES {#resources .unnumbered}

## 6.1 Prescribed Resources

### Textbook / Core Resource

**`{{Title}}`**

- **Author:** `{{Name}}`
- **Edition:** `{{Edition}}`
- **Publisher:** `{{Publisher}}`
- **Year:** `{{Year}}`
- **ISBN:** `{{ISBN}}`

## 6.2 Recommended Resources

```{r}
# Recommended readings
readings <- data.frame(
  Week = 1:12,
  Chapter = c("1", "2", "3-4", "5", "6", "7", "8", "9", "10", "11", "12", "Supplementary"),
  Topic = c(
    "Introduction", "Foundations", "Core Concepts",
    "Methodology", "Data Collection", "Analysis Basics",
    "Advanced Analysis", "Interpretation", "Reporting",
    "Case Studies", "Current Trends", "Professional Practice"
  ),
  `Additional Reading` = c(
    "`{{Reference}}`", "`{{Reference}}`", "`{{Reference}}`",
    "`{{Reference}}`", "`{{Reference}}`", "`{{Reference}}`",
    "`{{Reference}}`", "`{{Reference}}`", "`{{Reference}}`",
    "`{{Reference}}`", "`{{Reference}}`", "`{{Reference}}`"
  )
)

knitr::kable(readings, caption = "Weekly Readings")
```

::: {.note}
**Access:** All resources are available via Funda, SharePoint and the University Library.
:::

# 7. ASSESSMENT GUIDELINES {#assessment .unnumbered}

## 7.1 Assessment Overview and Matrix

**Total assessment weighting = 100%**

```{r}
# Assessment plan
assessment_plan <- data.frame(
  Assessment = c(
    "Test 1", "Practical Assignments (x3)", "Research Project",
    "Final Examination"
  ),
  Type = c("Individual", "Individual", "Group", "Individual"),
  Weight = c("15%", "30%", "25%", "30%"),
  `Due Date` = c(
    "Week 6", "Weeks 4, 8, 12", "Week 11", "Exam Period"
  ),
  `Learning Outcomes` = c("LO 1", "LO 2, 3", "LO 2, 3, 4", "All")
)

knitr::kable(assessment_plan, caption = "Assessment Plan (Total: 100%)")
```

## 7.2 Assessment Rules and Policies

### Pass Requirements and DP Rules

- **Duly Performed (DP) requirements:** `{{Specify requirements}}`
- **Pass mark:** `{{%}}` overall, with minimum `{{%}}` in final examination

### Late Submission Penalties

- Late submissions will incur a penalty of `{{%}}` per day
- Extensions must be requested `{{number}}` days before the due date

### Absence from Assessments

- Medical certificates required for absence from assessments
- Special assessments will be granted in accordance with university policy

::: {.warning}
**Important:** Please refer to Faculty and Institutional Assessment Policies for complete details on assessment procedures, including requirements for supplementary examinations.
:::

## 7.3 Assessment Criteria

### Research Project Rubric

| Criteria | Excellent (25-20) | Good (19-15) | Satisfactory (14-10) | Needs Improvement (9-0) |
|----------|-------------------|--------------|---------------------|------------------------|
| Research Design | Clear, well-justified design | Appropriate design | Basic design | Flawed design |
| Data Analysis | Sophisticated analysis | Appropriate methods | Basic analysis | Incorrect methods |
| Presentation | Professional, clear | Clear presentation | Adequate presentation | Poor presentation |
| Scientific Writing | Excellent writing, well-referenced | Good writing | Adequate writing | Poor writing |

# 8. REFERENCING STYLE {#referencing .unnumbered}

All written work must adhere to the **`{{e.g., APA 7th edition}}`** referencing style.

**Key Principles:**

- Acknowledge all sources used in your work
- Use in-text citations for quotes, paraphrases, and ideas
- Include a reference list at the end of assignments
- Use appropriate citation management tools (e.g., Zotero, Mendeley)

# 9. INFORMATION ABOUT TURNITIN {#turnitin .unnumbered}

All written assessments must be submitted via Turnitin. Similarity reports will be used as part of academic integrity checks.

**Turnitin Guidelines:**

- Submit your assignment before the due date
- Review your similarity report and make necessary revisions
- Similarity scores should be below `{{%}}` (excluding bibliography and quotes)

::: {.tip}
**Tip:** Submit your draft early to review the Turnitin report and make improvements before the final deadline.
:::

# 10. SUPPORT SERVICES & RESOURCES {#support .unnumbered}

## 10.1 The Library

The library offers extensive resources to support your learning.

**Contact Details:**

- **Website:** https://library.mandela.ac.za
- **Faculty Librarian:** `{{Name}}`
- **Email:** `{{Email}}`
- **Office Number:** `{{Location}}`

## 10.2 Emthonjeni - Fountain of Student Wellness

Emthonjeni Student Wellness consists of a team of professionally trained psychologists who are registered with the Health Professions Council of South Africa (HPCSA).

**Services offered:**

- Personal counseling
- Academic support
- Career guidance
- Mental health support

**General Contact Details:**

- **Office Hours:** Monday - Friday 08:00 - 16:30
- **Email:** emthonjeni@mandela.ac.za
- **Website:** https://emthonjeni.mandela.ac.za/

**Campus-Specific Contact:**

```{r}
# Campus contacts
campus_contacts <- data.frame(
  Campus = c("South", "North", "Missionvale", "Second Avenue"),
  Telephone = c(
    "041 504 2511", "041 504 3222",
    "041 504 1106", "041 504 3854"
  ),
  Email = c(
    "counselling.south@mandela.ac.za",
    "counselling.north@mandela.ac.za",
    "counselling.missionvale@mandela.ac.za",
    "counselling.2ndave@mandela.ac.za"
  )
)

knitr::kable(campus_contacts, caption = "Campus Contact Information")
```

# 11. GLOSSARY OF INSTRUCTION WORDS {#glossary .unnumbered}

```{r}
# Instruction words glossary
instruction_words <- data.frame(
  Word = c(
    "Analyse", "Compare", "Critically evaluate", "Define",
    "Describe", "Discuss", "Evaluate", "Explain", "Illustrate", "Justify"
  ),
  Meaning = c(
    "Break down into components and examine",
    "Show similarities and differences",
    "Assess the value/validity with reasons",
    "Give the exact meaning",
    "Give detailed features",
    "Examine by argument, debate, or reason",
    "Assess the value or importance",
    "Make clear, interpret, and spell out",
    "Use examples/diagrams to explain",
    "Give valid reasons or evidence"
  )
)

knitr::kable(instruction_words, caption = "Glossary of Instruction Words")
```

::: {.reflection}
**Reflection:** Understanding these instruction words will help you respond appropriately to assessment questions and tasks.
:::

---

**`{{Module Code}}` - `{{Academic Year}}`**

**Nelson Mandela University**

*Faculty of Science*

www.mandela.ac.za
